### 2011-05-06 Text/paper.tex
Finally steady-state is fulfilled. Pulled data from the cluster.

% TODO: This paragraph should be revisited, somehow it reads a little weirdly..
It should be noted that the binary liquid model we used has a uniform density. A part of discussion is
addressed in the introduction that to fully address the Bretherton problem one needs to take into
the account gravitational, viscous, inertial, and surface tension forces. Among all the works there is no full agreement between results even in the limit of Reynolds number $0$.  Moreover, as it was indicated by \citet{kreutzer-taylor} and by \citet{cerro-train} the pressure distribution, streamlines and bubble shape are strongly affected by the length of the liquid slug.  Though we try to eliminate

@@

\section{Binary liquid lattice Boltzmann model}
The lattice Boltzmann equation (LBE) operates on a rectangular grid representing the
physical domain. It utilizes
probability distribution functions (also known as particle populations)
containing information about
macroscopic variables, such as fluid density and momentum. LBE consists of
two parts: a local collision step, and a propagation step which transports
information from one node to another in certain
directions specified by a discrete velocity set.
The LBE is typically implemented as follows \cite{ginzburg-boundary-main}:
\begin{equation}
\label{standard:implementation}
\begin{aligned}
&f_i^{*}(\bm{x},t)=\omega f_i^{eq}(\bm{x},t)-(1-\omega) f_i(\bm{x},t) +
F_i,&&\text{collision step}\\
&f_i(\bm{x}+\bm{c_i},t+1)=f_i^{*}(\bm{x},t),&&\text{propagation step}\\
&g_i^{*}(\bm{x},t)=\omega_{\phi} g_i^{eq}(\bm{x},t)-(1-\omega_{\phi})
g_i(\bm{x},t),&&\text{collision step}\\
&g_i(\bm{x}+\bm{c_i},t+1)=g_i^{*}(\bm{x},t),&&\text{propagation step},
\end{aligned}
\end{equation}
where $\{f,g\}_i$ are the probability distribution functions in the direction $\bm{c_i}$, $\omega$
is the
relaxation parameter, $\omega_{\phi}$ is the phase relaxation parameter, and $F_i$ is the external
force population which
mimics the force behavior, Eq. \ref{full:navier:stokes}.

@@

The set of equations (\ref{set:equilibrium:binary}) restores the macroscopic
fluid equations as:
\begin{equation}
\label{full:navier:stokes}
\begin{aligned}
&\partial_t \rho+ \partial_{\alpha} \rho u_{\alpha}=0\\
&\rho\left(\partial_t+u_{\beta}\partial_{\beta}\right) u_{\alpha}=F_{\alpha}
-\partial_{\beta}P_{\alpha \beta} +
\nu\partial_{\beta}\left(\rho\partial_{\alpha}u_{\beta}+\rho\partial_{\beta} u_{\alpha}\right)\\
&\partial_t \phi + \partial_{\alpha} \phi u_{\alpha}=M \partial^2_{\beta\beta} \mu,
\end{aligned}
\end{equation}
where $\nu=c_s^2 (\tau-1/2)$ is the dynamic viscosity,
$M=\Gamma(\tau_{\phi}-1/2)$ is the mobility parameter, and $\tau=\frac{1}{\omega}$ and $\tau_{\phi}$
are the relaxation parameters of density and phase fields. The first equation of system
(\ref{standard:implementation}) simulates the continuity equation and the Navier-Stokes equation.
The lattice Boltzmann update rule for the second set $g_i$ simulates the phase propagation with the
supplied velocity from the Navier-Stokes equation.

@@

\section{Results}
\label{sec:results}
This section describes numerical simulations. One can refer to the Appendix~\ref{append:scaling} for
initialization and scaling procedures. The simulations were conducted on the following 
fluid domain grids $100 \times 100 \times 1500$, $160 \times 160 \times 1500$,
$160 \times 160 \times 2400$ and $200 \times 200 \times 3000$. Body forces were varied as
$\frac{\mathrm{d}P}{\mathrm{d}z}=10^{-6}-10^{-4}$. The binary-liquid model parameters were kept in
the stable region $k=A=0.004,0.04$. The relaxation rates were taken as $\tau_{\mathrm{liq}}=2.5$
and $\tau_{\mathrm{gas}}=0.7$ giving a gas-liquid dynamic viscosity ratio of $10$. The relaxation
parameter for the phase field was $\tau_{\phi}=1.0$.

@@

\subsection{Steady-state approach}
\label{sec:steady:state}
We performed different simulations to understand the number of steps required for the simulation to
settle down to a steady state. The grid to be simulated is $52 \times 52 \times 750$ which simulates
a quarter of the channel with the initial interface
width of $6.5$ lattice Boltzmann units together with the body force $\frac{\mathrm{d}P}{\mathrm{d}x}=1.6
\cdot 10^{-6}$. The simulation was performed for $140000$, $160000$, $180000$, $200000$,
$220000$ and
$240000$ iterations. The results are summarised in Table \ref{table:steady:state}. While the
capillary number varies only in the 4th digit, the radii are one percent accurate. 
\begin{table}
\begin{tabularx}{\textwidth}{|X|X|X|X|}
\hline
$N_{iter}$&$Ca$&$R_{axis}$&$R_{diag}$\\
\hline
$140000$&$0.1879$&$0.8657$&$0.8708$\\
$160000$&$0.1878$&$0.8650$&$0.8702$\\
$180000$&$0.1882$&$0.8647$&$0.8700$\\
$200000$&$0.1893$&$0.8645$&$0.8698$\\
$220000$&$0.1925$&$0.8644$&$0.8697$\\
$240000$&$0.1961$&$0.8645$&$0.8697$\\
\hline
\end{tabularx}
\caption{Results for the steady-state case. One
% TODO:structure?
can see that $200000$ steps are enough to structure
the bubble and approach the steady state. The small noise in the capillary number is connected to
the identification of the interface. One needs to address the interpolation and the spurious
currents existing in the system. All other parameters are relaxed to the
steady-state.\label{table:steady:state}}
\end{table}

>>>>

% TODO: This paragraph should be revisited, somehow it reads a little weirdly..
It should be noted that the binary liquid model we used has a uniform density. A part of discussion is
addressed in the introduction that to fully address the Bretherton problem one needs to take into
the account gravitational, viscous, inertial, and surface tension forces. Among all the works there
is no full 
agreement between results even in the limit of Reynolds number $0$.  Moreover, as it was indicated
by \citet{kreutzer-taylor} and by \citet{cerro-train} the pressure distribution, streamlines and
bubble shape are strongly affected by the length of the liquid slug and the length of the bubble. 
In current simulations we minimize the effects of bubbles train and inertia to have a least impact,
as the largest Reynolds number is not bigger than $10$ and the lengths of a bubble and a channel are
chosen to be as to minimize mutual effects of bubbles motion on each other and for the film
thickness to stabilize. However, more thorough studies are needed in order to understand precisely
the abovementioned effects.

@@

\section{Binary liquid lattice Boltzmann model}
The lattice Boltzmann equation (LBE) operates on a rectangular grid representing the
physical domain. It utilizes
probability distribution functions (also known as particle populations)
containing information about
macroscopic variables, such as fluid density and momentum. LBE consists of
two parts: a local collision step, and a propagation step which transports
information from one node to another in certain
directions specified by a discrete velocity set.
The LBE is typically implemented as follows \cite{ginzburg-boundary-main}:
\begin{equation}
\label{standard:implementation}
\begin{aligned}
&f_i^{*}(\bm{x},t)=\omega f_i^{eq}(\bm{x},t)-(1-\omega) f_i(\bm{x},t) +
F_i,&&\text{collision step}\\
&f_i(\bm{x}+\bm{c_i},t+1)=f_i^{*}(\bm{x},t),&&\text{propagation step}\\
&g_i^{*}(\bm{x},t)=\omega_{\phi} g_i^{eq}(\bm{x},t)-(1-\omega_{\phi})
g_i(\bm{x},t),&&\text{collision step}\\
&g_i(\bm{x}+\bm{c_i},t+1)=g_i^{*}(\bm{x},t),&&\text{propagation step},
\end{aligned}
\end{equation}
where $\{f,g\}_i$ are the probability distribution functions in the direction $\bm{c_i}$, $\omega$
is the
relaxation parameter, $\omega_{\phi}$ is the phase relaxation parameter, and $F_i$ is the external
force population which
mimics the force behavior.

@@

The set of equations (\ref{set:equilibrium:binary}) restores the macroscopic
fluid equations as:
\begin{equation}
\label{full:navier:stokes}
\begin{aligned}
&\partial_t \rho+ \partial_{\alpha} \rho u_{\alpha}=0\\
&\rho\left(\partial_t+u_{\beta}\partial_{\beta}\right) u_{\alpha}=F_{\alpha}
-\partial_{\beta}P_{\alpha \beta} +
\nu\partial_{\beta}\left(\rho\partial_{\alpha}u_{\beta}+\rho\partial_{\beta} u_{\alpha}\right)\\
&\partial_t \phi + \partial_{\alpha} \phi u_{\alpha}=M \partial^2_{\beta\beta} \mu,
\end{aligned}
\end{equation}
where $\nu=c_s^2 (\tau-1/2)$ is the kinematic viscosity,
$M=\Gamma(\tau_{\phi}-1/2)$ is the mobility parameter, and $\tau=\frac{1}{\omega}$ and $\tau_{\phi}$
are the relaxation parameters of density and phase fields. The first equation of system
(\ref{standard:implementation}) simulates the continuity equation and the Navier-Stokes equation.
The lattice Boltzmann equation for the second set $g_i$ simulates the phase propagation with the
supplied velocity from the Navier-Stokes equation.

@@

\section{Results}
\label{sec:results}
This section describes numerical simulations. One can refer to Appendix~\ref{append:scaling} for
initialization and scaling procedures. The simulations were conducted on the following 
fluid domain grids $100 \times 100 \times 1500$, $160 \times 160 \times 1500$,
$160 \times 160 \times 2400$ and $200 \times 200 \times 3000$. Body forces were varied as
$\frac{\mathrm{d}P}{\mathrm{d}z}=10^{-6}-10^{-4}$ lattice units. The binary-liquid model parameters
were kept in
the stable region $k=A=0.004,0.04$. The relaxation rates were taken as $\tau_{\mathrm{liq}}=2.5$
and $\tau_{\mathrm{gas}}=0.7$ giving a gas-liquid viscosity ratio of $10$. The relaxation
parameter for the phase field was $\tau_{\phi}=1.0$.

@@

\subsection{Steady-state approach}
\label{sec:steady:state}
We performed different simulations to understand the number of time steps required for the
simulation to
settle down to a steady state. The grid to be simulated is $52 \times 52 \times 750$ which simulates
a quarter of the channel with the initial interface
width of $6.5$ lattice Boltzmann units together with the body force $\frac{\mathrm{d}P}{\mathrm{d}x}=1.6
\cdot 10^{-6}$. The simulation was performed for $140000-250000$ iterations with the step of
$10000$ iterations. The results are summarised in Table \ref{table:steady:state}. While the
capillary number varies only in the 4th digit, the radii are one percent accurate. 
\begin{table}
\begin{tabularx}{\textwidth}{|X|X|X|X|}
\hline
$N_{iter}$&$Ca$&$R_{axis}$&$R_{diag}$\\
\hline
$140000$&$0.1879$&$0.8657$&$0.8708$\\
$150000$&$0.1879$&$0.8652$&$0.8704$\\
$160000$&$0.1878$&$0.8650$&$0.8702$\\
$170000$&$0.1880$&$0.8648$&$0.8701$\\
$180000$&$0.1882$&$0.8647$&$0.8700$\\
$190000$&$0.1885$&$0.8646$&$0.8699$\\
$200000$&$0.1893$&$0.8645$&$0.8698$\\
$210000$&$0.1963$&$0.8645$&$0.8697$\\
$220000$&$0.1925$&$0.8644$&$0.8697$\\
$230000$&$0.1936$&$0.8644$&$0.8697$\\
$240000$&$0.1961$&$0.8645$&$0.8697$\\
$250000$&$0.1932$&$0.8645$&$0.8698$\\
\hline
\end{tabularx}
\caption{Results for the steady-state case. One
can see that $200000$ steps are enough to shape
the bubble and approach the steady state. The small noise in the capillary number is connected to
the identification of the interface. One needs to address the interpolation and the spurious
currents existing in the system. All other parameters are relaxed to the
steady-state.\label{table:steady:state}}
\end{table}
